---
title: "Clicker Heroes Optimizer results"
output:
  pdf_document: default
  html_notebook: default
---

Values provided as input parameters:

AS  : ``r params$in_as``
HZE : ``r params$in_hze``


Values provided as control parameters:

Achievable levels of Ancients and limits of their respective parameters:
* Achievable level of Chronos: ``r params$chrono_l``
* Acceptable minimal boss time: ``r params$ti``
* Achievable level of Kumawakamaru: ``r params$kuma_l``
* Maximum number of monsters at end zone: ``r params$mo``
* Achievable level of Atman: ``r params$atman_l``
* Accaptable minimal primal boss chance: ``r params$pch``
* Achievable level of Dora: ``r params$dora_l``
* Acceptable minimal treasure chest chance: ``r params$cch``
* Limiting factor for Chronos, Atman and Dora effects: ``r params$limit``

***
Convergence zone: ``r params$desired_zone``

```{r, echo=FALSE}
inline_hook <- function(x) {
  if (is.numeric(x)) {
    format(x, digits = 2)
  } else x
}
knitr::knit_hooks$set(inline = inline_hook)

```

Distribution of Outsiders:
```{r 04_distribution, echo=FALSE, results='asis', paged.print=FALSE}
params$results
```
***
Relative costs of Xyliqil, Chor'gorloth, Phandoryss and Ponyboy against Borb, Rhageist, K'Ariqua, Orphalas and Sen-Akhan:
```{r 05_costs, echo=FALSE, results='asis', paged.print=FALSE}
params$costs
params$ratio
```
***
Detailed distribution of all effects through game zones (last 500 zones):
```{r 06_effects, echo=FALSE, results='asis', paged.print=FALSE}
params$effects%>% filter(., between(row_number(), n()-500, n()))
```
***
Distribution of boss timers:
```{r 07_time_distr, echo=FALSE, results='asis', paged.print=FALSE}
params$time_distr
```

Distribution of number of monsters:
```{r 08_monsters_distr, echo=FALSE, results='asis', paged.print=FALSE}
params$monsters_distr
```

Distribution of primal boss chance:
```{r 09_primal_ch_distr, echo=FALSE, results='asis', paged.print=FALSE}
params$primal_ch_distr
```

Distribution of treasure chest chance:
```{r 10_chest_ch_distr, echo=FALSE, results='asis', paged.print=FALSE}
params$chest_ch_distr
```

